---
title: "AD Plant Sites in Suffolk"
scctemplate:
  header:
    site_branding: "Suffolk County Council"
  navigation:
    breadcrumb_trail:
      - text: "Home"
  seo:
    description: "SEO (search engine optimisation) description"
    keywords: "SEO, keywords, comma, separated"
toc: false
---
```{r setup, include = FALSE}
library(sf)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(mapview)
library(leafem)
library(gt)
```

## Anaerobic Digestion
Anaerobic digestion facilities promote anaerobic degradation of organic wastes 
such as animal wastes, energy crops, and vegetable tailings. The process 
involves introducing the feedstock into a tank of bacteria rich slurry. This 
process produces methane gas that is normally used to drive a diesel generator 
and export the electricity to the grid. The main advantage of this over 
composting is that electrical power is produced. Co-locating with sewage 
treatment allows methane to be recovered from sewage and at the same time 
prevents a potent greenhouse gas from escaping into the atmosphere.

## Policy WP7
Anaerobic digestion facilities may be acceptable on land:

  a) within the uses identified within Policy WP3; or
  b) integrated with waste water treatment plants.

Proposals for such facilities at landfill sites may be considered acceptable on a 
temporary basis whilst landfilling and restoration is taking place on site.
Proposals must also comply with the environmental criteria set out in Policy 
GP4.

# List of sites

Below are the sites listed in the Suffolk Minerals & Waste Local Plan, adopted in July 2020.

## Anaerobic Digesion sites
```{r table, echo = FALSE, warning = FALSE, out.width = "100%", fig.align='left'}
ad_plants <- data.frame(
  eastings = c(
    625406,
    579489,
    648331,
    640294,
    596243,
    635649
  ),
  northings = c(
    273627,
    265335,
    277563,
    279245,
    238477,
    253229
  ),
  site_name = c(
    "Barley Brigg Biogas Ltd",
    "Symonds Farm Anaerobic Digestion Plant",
    "Adnams Distribution Plant",
    "Bernard Matthews",
    "Hill Farm, Boxford",
    "Bentwaters Park AD Plant"
  ),
  operator = c(
    "Barley Brigg Biogas Ltd",
    "Symonds Farm Power Ltd",
    "Bio Group Ltd",
    "Houlton Renewable Power",
    "Boxford (Suffolk) Farms",
    "Agri-Gen"
  )
)



ad_plants |> 
  gt()
```

## Water Recycling Centres

```{r table_water, echo = FALSE, warning = FALSE, out.width = "100%", fig.align='left'}
water_plants <- data.frame(
  eastings = c(
    646061,
    634283,
    616401,
    618594,
    620993,
    605502,
    587246,
    578076,
    639439,
    644703
  ),
  northings = c(
    260233,
    241444,
    235918,
    254790,
    262928,
    267475,
    279446,
    263708,
    289608,
    290417
  ),
  site_name = c(
    "Aldeburgh Stw",
    "Alderton Stw",
    "Alton Water Stw-Private Altows",
    "Ashbocking-Mill Field Stw",
    "Ashfield-Sunnyside Cr Stw",
    "Bacton Finingham La Stw",
    "Badwell Ash Stw",
    "Barnham Stw",
    "Barrow Stw",
    "Barsham Stf (Suffolk)"
  ),
  operator = c(
    "Anglian Water",
    "Anglian Water",
    "Anglian Water",
    "Anglian Water",
    "Anglian Water",
    "Anglian Water",
    "Anglian Water",
    "Anglian Water",
    "Anglian Water",
    "Anglian Water"
  )
)

water_plants |> 
  gt()
```

# Interactive Map of Site Locations

The information above is plotted on an interactive map here. Hover over the markers to get more information.

```{r map, echo = FALSE, warning = FALSE, out.width = "100%", fig.align='center'}
sf_plants <- st_as_sf(ad_plants, coords = c("eastings", "northings"), crs = 27700)
sf_plants <- st_transform(sf_plants, 4326)

sf_water <- st_as_sf(water_plants, coords = c("eastings", "northings"), crs = 27700)
sf_water <- st_transform(sf_water, 4326)

  ff <- leaflet() |> 
  addTiles() |> 
  addCircleMarkers(
    data = sf_plants,
    label = sf_plants$site_name,
    color = "#e8850c"
  ) |> 
  addCircleMarkers(data = sf_water,
             label = sf_water$site_name,
             color = "#2d6ca2") |> 
    addLegend(
      colors = c("#e8850c", "#2d6ca2"),
      labels = c("AD Plants", "Water Recycling Centres")
    )

ff
```
