---
title: "Interactive Map of Waste Locations of Interest"
scctemplate:
  header:
    site_branding: "Suffolk County Council"
  navigation:
    breadcrumb_trail:
      - text: " Interactive Map of Waste Locations of Interest"
    toc:
      sticky: false
      numbered: false
---
```{r setup, include = FALSE}
library(sf)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(mapview)
library(leafem)
library(gt)
library(leaflet.extras)
library(DT)
```

This interactive map displays all Waste Sites, Mineral Extraction Sites and Anglian Water sites in Suffolk. It is based on data from 2018, so some information is not up to date (for example, Mason's Landfill is now operated by Valencia Waste Management Ltd, and not Viridor Waste Disposal Ltd).

Hover over each site to get information on the name, operator and type of sites. Individual sites can be searched for by clicking on the lens icon. You can display this map full screen with the rectangle icon. 

In the bottom right, you can change the map background, and tick different boxes to include/exclude different types of sites. **The Consultation Area is hidden by default**, and can be switched on here.

For Anglian Water Sites, the site boundaries were not available. Therefore these sites are displayed as points only.

For some Mineral and Waste Extraction Sites, no site name and operator is provided. This is a problem in the underlying data.

# Interactive Map

```{r map, echo = FALSE, warning = FALSE, message = FALSE, out.width = "100%", fig.align='center'}
waste_dir <- "L:\\MAPINFO\\DATA\\data_new\\minerals and waste\\Minerals and Waste GIS\\"

# Mineral Consulation Area
consultation_area <- st_read(paste0(waste_dir, "Minerals Consultation Area.TAB"), drivers = "MapInfo File", quiet = TRUE)
consultation_area <- st_transform(consultation_area, 4326)

# waste sites
site_types <- list.files(waste_dir, "*.TAB", recursive = TRUE)

site_types <- site_types[!grepl("combined", site_types)]
site_types <- site_types[!grepl("Buffer", site_types)]
site_types <- site_types[!grepl("Minerals Consultation Area", site_types)]

sites <- lapply(site_types, function(names) {
  sites <- st_read(paste0(waste_dir, names), quiet = TRUE)
  sites$type <- names
  return(sites)
})

sites <- dplyr::bind_rows(sites)

sites$type <- gsub(".TAB", "", sites$type)
sites$type <- gsub("2", "", sites$type)
sites$type <- gsub("1", "", sites$type)
sites$type <- gsub("_", "", sites$type)
sites$type <- gsub("Miscillaneous", "Miscellaneous", sites$type)
sites$type <- gsub("Secondary Aggregate Recycling Sites", "Secondary Aggregate Recycling", sites$type)
sites$type <- gsub("Current", "Permitted", sites$type)
sites$type <- gsub("Proposed", "Allocated", sites$type)

# Remove recursive folder names
sites$type <- regmatches(sites$type, gregexpr("(?<=/).*", sites$type, perl=TRUE))

# Adding in anglian water sites
aw_sites_csv <- readr::read_csv("C://Documents//ad-sites//anglian_water_sites.csv")
aw_sites_csv$type <- "Anglian Water Site"

colnames(aw_sites_csv) <- c("Site_Ref", "Site_Name", "Operator", "Easting", "Northing", "type")
aw_sites <- st_as_sf(aw_sites_csv, coords = c("Easting", "Northing"), crs = 27700)

# Convert to osgb, we need 1km buffer
# st_buffer needs to be used in the units of st_crs(x)$units
sites_buffer <- st_buffer(sites, dist = 250)
aw_buffer <- st_buffer(aw_sites, dist = 400)

sites_buffer <- st_union(aw_buffer, sites_buffer)

# Combine buffers if they overlap
sites_buffer <- sites_buffer %>% 
  st_union() %>% 
  st_cast('POLYGON')

sites <- st_transform(sites, 4326)
aw_sites <- st_transform(aw_sites, 4326)

sites_buffer <- st_transform(sites_buffer, 4326)

# quick fix - remove Wangford extension
sites <- sites |> 
  dplyr::filter(Site_Name != "Wangford Extension")

mineral_types <- c(
  "Permitted Mineral Extraction Sites",
  "Allocated Mineral Extraction Sites",
  "Asphalt Plants",
  "Concrete Batching Plants",
  "Concrete Products Sites",
  "Mineral Extraction Sites",
  "Mineral Railheads",
  "Mineral Wharves"
)

sites$type <- as.character(sites$type)

mineral_sites <- sites |> 
  dplyr::filter(type %in% mineral_types)

sites <- sites |> 
  dplyr::filter(!type %in% mineral_types)

# HTML labels
labels <- sprintf(
  "<strong>%s - %s</strong><br/><strong>%s</strong><br/> %s",
  sites$Site_Ref, sites$Site_Name, sites$Operator, sites$type
) %>% lapply(htmltools::HTML)

mineral_labels <- sprintf(
  "<strong>%s - %s</strong><br/><strong>%s</strong><br/> %s",
  mineral_sites$Site_Ref, mineral_sites$Site_Name, mineral_sites$Operator, mineral_sites$type
) %>% lapply(htmltools::HTML)

aw_labels <- sprintf(
  "<strong>%s - %s</strong><br/><strong>%s</strong><br/> %s",
  aw_sites$Site_Ref, aw_sites$Site_Name, aw_sites$Operator, aw_sites$type
) %>% lapply(htmltools::HTML)

mineral_map <- leaflet() |> 
  addTiles(group = "Topo") |> 
  addTiles(
    urlTemplate = "https://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}",
    group = "Satellite"
  ) |> 
  leaflet::addPolygons(
    data = sites,
    group = sites$type,
    color = "black",
    opacity = 1,
    weight = 2,
    fillColor = "#e8850c",
    fillOpacity = 0.2,
    highlightOptions = highlightOptions(
      color = "white",
      weight = 4,
      fill = "#666",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weigth" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"
    ),
  ) |> 
  leaflet::addPolygons(
    data = mineral_sites,
    group = mineral_sites$type,
    color = "black",
    opacity = 1,
    weight = 2,
    fillColor = "#2d6ca2",
    fillOpacity = 0.2,
    highlightOptions = highlightOptions(
      color = "white",
      weight = 4,
      fill = "#666",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = mineral_labels,
    labelOptions = labelOptions(
      style = list("font-weigth" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"
    ),
  ) |> 
  leaflet::addCircles(
    data = aw_sites,
    group = aw_sites$type,
    color = "black",
    opacity = 1,
    weight = 2,
    fillColor = "#e2eefa",
    fillOpacity = 0.2,
    highlightOptions = highlightOptions(
      color = "white",
      weight = 4,
      fill = "#666",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = aw_labels,
    labelOptions = labelOptions(
      style = list("font-weigth" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"
    ),
  ) |> 
  leaflet::addPolygons(
    data = sites_buffer,
    color = "black",
    opacity = 1,
    weight = 2,
    fill = FALSE,
    group = "Buffers"
  ) |> 
  leaflet::addPolygons(
    data = consultation_area,
    color = "black",
    opacity = 1,
    weight = 2,
    fill = "#666",
    fillOpacity = 0.1,
    group = "Consultation Area"
  ) |> 
  addLayersControl(
    data = sites,
    baseGroups = c("Topo", "Satellite"),
    overlayGroups = c(
      "Consultation Area",
      "Buffers",
      aw_sites$type,
      mineral_sites$type,
      sites$type
    ),
    position = "bottomright"
  ) |> 
  hideGroup("Consultation Area") |> 
  addLegend(
    colors = c("#e8850c", "#2d6ca2", "#e2eefa", "#666"),
    labels = c("Waste Sites", "Mineral Extraction Sites", "Anglian Water Sites", "Consultation Area")
  ) |>
  addSearchFeatures(
    targetGroups = c(sites$type, mineral_sites$type, aw_sites$type),
    options = searchFeaturesOptions(
      hideMarkerOnCollapse = TRUE
    )) |> 
  addFullscreenControl()

htmlwidgets::saveWidget(mineral_map, "mineral_map.html")

htmltools::tags$iframe(
  src = "mineral_map.html",
  width = "100%",
  style="height: 75vh;",
  scrolling = "no"
)

```

# Full list of sites

Below is the full list of sites mapped above, by type of site.

## Anglian Water Sites

```{r aw_sites, echo = FALSE, warning = FALSE, message = FALSE, out.width = "100%", fig.align='center'}

aw_sites_csv <- aw_sites_csv |> 
  dplyr::select(Ref = Site_Ref, `Site Name` = Site_Name, Operator, Easting, Northing)

datatable(
  aw_sites_csv,
  extensions = "Buttons",
  rownames = FALSE,
  options = list(
    dom = "Bfrtip",
    buttons = c("copy", "csv", "excel", "pdf", "print")
  )
)

```

## All other sites

```{r waste_sites, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", out.width = "100%", fig.align='left'}

display_sites <- sites |> 
  as.data.frame() |> 
  dplyr::select(Ref = Site_Ref, `Site Name` = Site_Name, Operator, Type = type, Easting, Northing)

datatable(
  display_sites,
  extensions = "Buttons",
  rownames = FALSE,
  options = list(
    dom = "Bfrtip",
    buttons = c("copy", "csv", "excel", "pdf", "print")
  )
)
```
